### 2018-05-10 Manuscript/manuscript.Rmd
About to revamp theory in manuscript

---
title: ''
author: ''
header-includes:
- \usepackage[T1]{fontenc}
- \usepackage{microtype}
- \usepackage[margin=1in]{geometry}
- \usepackage{fancyhdr}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead{}
- \fancyfoot{}
- \fancyhead[C]{Multiple Outcomes}
- \fancyfoot[RO,LE]{\thepage}
- \usepackage{booktabs}
- \usepackage{lettrine}
- \usepackage{paralist}
- \usepackage{setspace}\singlespacing
- \usepackage{url}
- \usepackage{parskip}
- \usepackage{color,soul}
- \usepackage{palatino}
- \usepackage{amsmath,amsfonts,amsthm, textcomp}
- \usepackage{bm}
- \usepackage{caption}
- \usepackage{subcaption}
- \usepackage{tikz}
- \usepackage{verbatim}
- \usetikzlibrary{matrix}
- \usepackage{float}
output: pdf_document
bibliography: refs_fake.bib
csl: aje_style.csl
---

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}
\newtheorem{example}{Example}
\newtheorem{algorithm}{Algorithm}

<!--
\doublespacing

\begin{center}
\textbf{ \LARGE{Title line one:} } \\ \vspace{5mm}
\textbf{ \LARGE{title line two} }
\vspace{10mm}
\end{center}

@@

\vspace{10mm}
\begin{center}
\large{ \emph{ Maya B. Mathur$^{1, 2\ast}$, Peng Ding$^{3}$, and Tyler J. VanderWeele$^{1,4}$ } }
\end{center}

@@

\newpage
-->

\section{Notes to self}

@@

Suppose that $K$ random variables are measured on $N$ subjects, with the resulting matrix denoted $\mathbf{Z} \in \mathbb{R}_{N \times K}$. Let $Z_{nk}$ denote, for the $n^{th}$ subject, the $k^{th}$ random variable. Consider a bootstrapping algorithm (which is defined below) that generates, for iterate $j$, a dataset containing the random variables $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ for each subject $n$. There are a total of $B$ bootstrapped datasets.

We refer to probability density functions as $f$ and cumulative distribution functions as $F$. Specifically, we refer to the joint distribution of the data as follows. With $\mathcal{B} \in \mathbb{R}_{N \times K}$ denoting a matrix of constants with entries $\left( b_{11}, \dotsb, b_{NK} \right)$, let:
\begin{align*}
F_{\mathbf{Z}} \left( \mathbf{B} \right) &= P \left( Z_{11} \le b_{11}, \dotsb, Z_{NK} \le b_{NK} \right)
\end{align*}

<!-- Define the joint CDF of $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ as:

\begin{align*}
F_{\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)} \left( r_1, \dotsb, r_K \right) &= P \left( Z_{n1}^{(j)} < r_1, \dotsb, Z_{nK}^{(j)} < r_K \right)
\end{align*}
-->

We will usually refer simply to $\mathbf{Z}$ and $F_{\mathbf{Z}}$ for brevity and will denote their counterparts in bootstrapped dataset $j$ as $\mathbf{Z}^{(j)}$ and $F_{\mathbf{Z}^{(j)}}$.

Further suppose that we conduct $W$ hypothesis tests, each with level $\alpha$. Let $c_{w,\alpha}$ be the critical value for the test statistic, $T_w$, of the $w^{th}$ test. We refer to the vector of test statistics as $\mathbf{T}$. Assume that each test concerns a point null hypothesis (\textbf{Assumption 1}), that each test statistic is a continuous function of the data with continuous first derivatives, $\mathbf{Z}$ (\textbf{Assumption 2}), and that each test is parametric with consistent estimates of all parameters in the likelihood identifiable from the observed data (\textbf{Assumption 3}). We define the "strong null" as the case in which all $W$ point null hypotheses hold and use the superscript $^0$ to denote variables generated under the strong null.

Define the statistic corresponding to the total number of rejections in $W$ tests in a sample generated under the strong null as $\widehat{\theta}^0 = \sum_{w=1}^W 1 \big\{ T_w^0 > c_{w,\alpha} \big\}$. Similarly, the total number of rejections in bootstrap sample $j$ is $\widehat{\theta}^{(j)} = \sum_{w=1}^W 1 \big\{ T_w^{(j)} > c_{w,\alpha} \big\}$.

Respectively define the true distribution of the number of rejections under the strong null, its counterpart in the bootstrap samples, and its empirical estimator in the bootstrap samples as:
\begin{align*}
F_{\widehat{\theta}^0}(r) &= P \left( \widehat{\theta}^0 \le r \right) \\
F_{\widehat{\theta}^{(j)}}(r) &= P \left( \widehat{\theta}^{(j)} \le r \right) \\
\widehat{F}_{\widehat{\theta}^{(j)}} \left( r \right) &= \frac{1}{B} \sum_{j^{*}=1}^B 1 \Big\{ \widehat{\theta}^{(j^{*})} \le r \Big\}
\end{align*}

@@

\section{Results}

We now show that under a parametric bootstrapping algorithm defined below, the empirical distribution of the number of rejections in the bootstrap samples converges in distribution to the true distribution of the number of rejections in sample generated under the strong null. Figure \ref{roadmap} depicts the structure of the proofs.

\begin{figure}[H]
\caption{Overview of theory to follow. The dashed arrows denote convergence in probability in either $N$ or both $N$ and $B$. The solid arrow denotes almost sure convergence in $B$. Parenthetical acronyms refer to remarks, a lemma, and a theorem developed below.}
\label{roadmap}
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     F_{ \mathbf{T}^{(j)} } & F_{ \mathbf{T}^0 } \\
      %& F_{ \mathbf{Z} }
      \\};
  \path[-stealth]
  % the - argument removes the arrowhead
    (m-1-1) edge[dashed] node [below] {(R1)} (m-1-2)

@@

    %(m-1-2) edge[dotted] node [right] {(L2)} (m-2-2)
            ;
\end{tikzpicture} % pic 1
\qquad
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     F_{ \widehat{\theta}^{(j)} } & F_{ \widehat{\theta}^0 }  \\
      \widehat{F}_{ \widehat{\theta}^{(j)} } & \\};
  \path[-stealth]
  % the - argument removes the arrowhead
    (m-1-1) edge[dashed] node [below] {(L1)} (m-1-2)

    % diagonal line
	(m-2-1) edge[] node [left] {(R2)} (m-1-1)

    (m-2-1) edge [dashed] node [below] {(T1)} (m-1-2)
            ;
\end{tikzpicture}
\end{center}
\end{figure}

<!-------------- Definition 1 --------------->
\bigskip \begin{algorithm}[Parametric bootstrap under the strong null] 
\label{cbt_def}
We will refer throughout to bootstrap samples generated as follows:
\begin{enumerate}
\item Use the observed data to obtain consistent point estimates of any unknown parameters in the likelihood. 
\item For any parameters in the likelihood that are constrained under the null hypothesis, set them equal to their null values (which are uniquely defined under Assumption 1 regarding point null hypotheses). For nuisance parameters, set them equal to their consistent estimates.  
\item For any covariates treated as fixed in the likelihood, set them equal to their observed values.
\item Generate outcome data from the estimated likelihood under the strong null as defined above. 
\end{enumerate}
\end{algorithm}

(\hl{CITE ME - e.g., Fox, Romano}.)
Note that unlike some resampling schemes that can induce \hl{XXX} problems, this algorithm guarantees that the bootstrapped data satisfy all parametric assumptions of the hypothesis tests to be conducted, preserving the nominal $\alpha$ of each test.

<!-------------- Example 1 --------------->
\bigskip
\begin{example}[Parametric bootstrap for multiple linear regression] 
Suppose that one of the hypothesis tests is conducted using an OLS model regressing the $w^{th}$ variable on the first variable, adjusting for the second variable:
$$Z_{nw} = \beta_0 + \beta_1 Z_{n1} + \beta_2 Z_{n2} + \epsilon_{nw}$$
with $H_0: \beta_1 = 0$ and $\epsilon \sim N(0, \sigma^2)$. Then we can apply Algorithm \ref{cbt_def} as follows:
\begin{enumerate}
\item Fit the model to the observed data to estimate the three nuisance parameters as $\widehat{\beta}_0$, $\widehat{\beta}_2$, and $\widehat{\sigma}^2$. 
\item For each bootstrap iterate, set the design matrix equal to that of the observed data.
\item Set $\beta_1 = 0$ (invoking the strong null), and set nuisance parameters $\beta_0 = \widehat{\beta}_0$, $\beta_2 = \widehat{\beta}_2$, and $\sigma^2 = \widehat{\sigma}^2$. 
\item Thus, for each bootstrap iterate, generate the bootstrapped outcomes as $Z_{nw}^{(j)} = \widehat{\beta}_0 + \widehat{\beta}_2 Z_{n2} + \epsilon^{(j)}_{nw}$, where $\epsilon^{(j)}_{nw} \sim N(0,\widehat{\sigma}^2)$. 
\end{enumerate}
\end{example}

<!-------------- Example 2 --------------->
\bigskip
\begin{example}[Parametric bootstrap for linear mixed model] 
The approach in Definition \ref{cbt_def} can accommodate parametric models with correlated observations, such as a linear mixed model with random intercepts by subject. One could obtain consistent estimates of the random intercepts using, for example, empirical Bayesian estimation, and these estimates can be plugged into the estimated likelihood under the strong null. 
\end{example}

<!-------------- Remark 1 --------------->
\bigskip
\begin{remark}
\label{CMT_results}
The distribution of the bootstrapped test statistics is consistent in $N$ for the true distribution of the test statistics under the strong null. By repeatedly invoking the Continuous Mapping Theorem (CMT):
\begin{align}
\label{consistent}
f_{\mathbf{Z}^{(j)}} &\xrightarrow[N \to \infty]{P} f_{\mathbf{Z}^0} \tag{CMT; Assumption 3} \\
f_{\mathbf{T}^{(j)}} &\xrightarrow[N \to \infty]{P} f_{\mathbf{T}^0} \tag{CMT; Assumption 2} \\
F_{\mathbf{T}^{(j)}} &\xrightarrow[N \to \infty]{P} F_{\mathbf{T}^0} \tag{CMT; integration preserves continuity} \\
\end{align}
\end{remark}

<!-------------- Remark 2 --------------->
\bigskip \begin{remark}
\label{glivenko}
By the i.i.d construction of the bootstrap samples and the Glivenko-Cantelli theorem, the empirical distribution of the number of rejections in the bootstrap samples converges almost surely in $B$ to its true distribution under the strong null:
$$\widehat{F}_{\widehat{\theta}^{(j)}} \xrightarrow[B \to \infty]{A.S.} F_{\widehat{\theta}^{(j)}} $$
\end{remark}

@@

<!-------------- Lemma 1 --------------->
\bigskip \begin{lemma}
\label{lemma3}
The number of rejections in the bootstrap samples converges in distribution in $N$ to the number of rejections in samples from the original population under the strong null: $$F_{{ \widehat{\theta} }^{(j)}} \xrightarrow[N \to \infty]{P} F_{{ \widehat{\theta} }^0}$$

@@

\bigskip Now consider the distribution of $\widehat{\theta}^{(j)}$:
\begin{align*}
P \left( \widehat{\theta}^{(j)} = r \right) &= P \left( \sum_{w=1}^W 1 \Big\{ T_w^{(j)} > c_{w,\alpha} \Big\} = r \right) \\
&= \sum_{ \left( A_1, \dotsb, A_W \right) \in \mathcal{A} } P \left( T_1^{(j)} \in A_1, \dotsb, T_W^{(j)} \in A_W \right) \\
&\xrightarrow[N \to \infty]{P} \sum_{ \left( A_1, \dotsb, A_W \right) \in \mathcal{A} } P \left( T^0_1 \in A_1, \dotsb, T^0_W \in A_W \right) \tag{\text{from Remark} \ref{CMT_results}}\\
&= P \left( \widehat{\theta}^0 = r \right)
\end{align*}
\end{proof}
\end{lemma}

<!-------------- Theorem 1 --------------->
\bigskip \begin{theorem} 
\label{theorem1}
The empirical distribution of the number of rejections in the bootstrap samples is consistent in $N$ and $B$ for the true distribution of the number of rejections under the strong null:
$$\widehat{F}_{\widehat{\theta}^{(j)}} \xrightarrow[B, N \to \infty]{P} F_{\widehat{\theta}^0} $$
\begin{proof}
Fix an arbitrarily small $\epsilon > 0$ and $\epsilon' > 0$. Remark \ref{glivenko} implies consistency, so there exists a $B^{*}$ such that, for all $B > B^{*}$:
\begin{align*}
P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon / 2 \right) &< \epsilon'/2
\end{align*}
Similarly, from Lemma \ref{lemma3}, there exists an $N^{*}$ such that, for all $N > N^{*}$:
\begin{align*}
P \left( \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon / 2 \right) &< \epsilon' / 2
\end{align*}
Thus, for all $B$ and $N$ such that $B > B^{*}$ and $N > N^{*}$:
\begin{align*}
P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right) &= P \left( \vert  \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } + F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right) \\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert + \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right)  \tag{triangle inequality}\\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon/2 \; \text{ or } \; \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon/2 \right) \\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon/2 \right) + P \left( \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon/2 \right) \\
&< \epsilon' 
\end{align*}
\end{proof}
\end{theorem}

>>>>

---
title: ''
author: ''
output:
  pdf_document: default
  word_document: default
header-includes:
- \usepackage[T1]{fontenc}
- \usepackage{microtype}
- \usepackage[margin=1in]{geometry}
- \usepackage{fancyhdr}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead{}
- \fancyfoot{}
- \fancyhead[C]{Multiple Testing}
- \fancyfoot[RO,LE]{\thepage}
- \usepackage{booktabs}
- \usepackage{lettrine}
- \usepackage{paralist}
- \usepackage{setspace}\singlespacing
- \usepackage{url}
- \usepackage{parskip}
- \usepackage{color,soul}
- \usepackage{palatino}
- \usepackage{amsmath,amsfonts,amsthm, textcomp}
- \usepackage{bm}
- \usepackage{caption}
- \usepackage{subcaption}
- \usepackage{tikz}
- \usepackage{verbatim}
- \usetikzlibrary{matrix}
- \usepackage{float}
bibliography: refs_mo.bib
csl: apa_style.csl
---

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}
\newtheorem{example}{Example}
\newtheorem{assump}{Assumption}

@@

\begin{center}
\textbf{ \LARGE{Multiple Testing Research Update \#1} } \\ \vspace{5mm}
\textbf{ \LARGE{\today} }
\vspace{10mm}
\end{center}

\tableofcontents

<!--
\vspace{10mm}
\begin{center}
\large{ \emph{ Maya B. Mathur$^{1, 2\ast}$, Peng Ding$^{3}$, and Tyler J. VanderWeele$^{1,4}$ } }
\end{center}

@@

-->

\newpage

@@

Suppose that $K$ random variables are measured on $N$ subjects, with the resulting matrix denoted $\mathbf{Z} \in \mathbb{R}_{N \times K}$. Let $Z_{nk}$ denote, for the $n^{th}$ subject, the $k^{th}$ random variable. Consider a resampling algorithm that generates, for iterate $j$, a dataset containing the random vector $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ for each subject $n$. There are a total of $B$ resampled datasets. We use the superscript $^{(j)}$ to denote random variables, distributions, and statistics in resampled dataset $j$.

Further suppose that we conduct $W$ hypothesis tests, each with level $\alpha$. Denote the $w^{th}$ null hypothesis as $H_{0w}$. Let $c_{w,\alpha}$ be the critical value for the test statistic, $T_w$, of the $w^{th}$ test. We refer to the vector of test statistics as $\mathbf{T}$. <!--Assume that each test concerns a point null hypothesis (\textbf{Assumption 1}) and that each test is parametric with consistent estimates of the tested parameters in the likelihood identifiable from the observed data (\textbf{Assumption 2}).--> We define the "strong null" as the case in which all $W$ point null hypotheses hold and use the superscript $^0$ generally to denote distributions, data, or statistics generated under the strong null.

Define the statistic corresponding to the total number of rejections in $W$ tests in a sample generated under the strong null as $\widehat{\theta}^0 = \sum_{w=1}^W 1 \big\{ T_w^0 > c_{w,\alpha} \big\}$. Similarly, the total number of rejections in resample $j$ is $\widehat{\theta}^{(j)} = \sum_{w=1}^W 1 \big\{ T_w^{(j)} > c_{w,\alpha} \big\}$. Using $F$ to denote cumulative distribution functions, respectively define the true CDF of the number of rejections under the strong null, its counterpart in the resamples, and its empirical estimator in the resamples as:
\begin{align*}
F_{\widehat{\theta}^0}(r) &= P \left( \widehat{\theta}^0 \le r \right) \\
F_{\widehat{\theta}^{(j)}}(r) &= P \left( \widehat{\theta}^{(j)} \le r \right) \\
\widehat{F}_{\widehat{\theta}^{(j)}} \left( r \right) &= \frac{1}{B} \sum_{j^{*}=1}^B 1 \Big\{ \widehat{\theta}^{(j^{*})} \le r \Big\}
\end{align*}

<!----- Old version
\section{Setting and notation}

Suppose that $K$ random variables are measured on $N$ subjects, with the resulting matrix denoted $\mathbf{Z} \in \mathbb{R}_{N \times K}$. Let $Z_{nk}$ denote, for the $n^{th}$ subject, the $k^{th}$ random variable. Consider a resampling algorithm that generates, for iterate $j$, a dataset containing the random vector $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ for each subject $n$. There are a total of $B$ resampled datasets.

We refer to cumulative distribution functions as $F$. Specifically, we refer to the joint distribution of the data as follows. With $\mathcal{B} \in \mathbb{R}_{N \times K}$ denoting a matrix of constants with entries $\left( b_{11}, \dotsb, b_{NK} \right)$, let:
\begin{align*}
F_{\mathbf{Z}} \left( \mathbf{B} \right) &= P \left( Z_{11} \le b_{11}, \dotsb, Z_{NK} \le b_{NK} \right)
\end{align*}

Define the joint CDF of $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ as:

\begin{align*}
F_{\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)} \left( r_1, \dotsb, r_K \right) &= P \left( Z_{n1}^{(j)} < r_1, \dotsb, Z_{nK}^{(j)} < r_K \right)
\end{align*}

We will usually refer simply to $\mathbf{Z}$ and $F_{\mathbf{Z}}$ for brevity and will denote their counterparts in resampled dataset $j$ as $\mathbf{Z}^{(j)}$ and $F_{\mathbf{Z}^{(j)}}$.

Further suppose that we conduct $W$ hypothesis tests, each with level $\alpha$. Let $c_{w,\alpha}$ be the critical value for the test statistic, $T_w$, of the $w^{th}$ test. We refer to the vector of test statistics as $\mathbf{T}$. Assume that each test concerns a point null hypothesis (\textbf{Assumption 1}) and that each test is parametric with consistent estimates of the tested parameters in the likelihood identifiable from the observed data (\textbf{Assumption 2}). We define the "strong null" as the case in which all $W$ point null hypotheses hold and use $F_{ \mathbf{Z}^0 }$ to denote the distribution of the data under the strong null. We use the superscript $^0$ generally to denote data or statistics generated under the strong null.

Define the statistic corresponding to the total number of rejections in $W$ tests in a sample generated under the strong null as $\widehat{\theta}^0 = \sum_{w=1}^W 1 \big\{ T_w^0 > c_{w,\alpha} \big\}$. Similarly, the total number of rejections in resample $j$ is $\widehat{\theta}^{(j)} = \sum_{w=1}^W 1 \big\{ T_w^{(j)} > c_{w,\alpha} \big\}$.

Respectively define the true distribution of the number of rejections under the strong null, its counterpart in the resamples, and its empirical estimator in the resamples as:
\begin{align*}
F_{\widehat{\theta}^0}(r) &= P \left( \widehat{\theta}^0 \le r \right) \\
F_{\widehat{\theta}^{(j)}}(r) &= P \left( \widehat{\theta}^{(j)} \le r \right) \\
\widehat{F}_{\widehat{\theta}^{(j)}} \left( r \right) &= \frac{1}{B} \sum_{j^{*}=1}^B 1 \Big\{ \widehat{\theta}^{(j^{*})} \le r \Big\}
\end{align*}

------->

@@

\section{Main results}

We now show that under a certain class of resampling algorithms defined below, the empirical distribution of the number of rejections in the resamples converges to the true distribution of the number of rejections in samples generated under the strong null. Figure \ref{roadmap} depicts the structure of the proofs.

\begin{figure}[H]
\caption{Overview of theory to follow. Solid arrows denote ordinary limits in $B$, the dashed line denotes almost sure convergence in $N$, and the dotted line denotes convergence in probability in both $N$ and $B$. Parenthetical acronyms refer to an assumption, remark, lemma, and theorem developed below.}
\label{roadmap}
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     F_{ \mathbf{T}^{(j)} } & F_{ \mathbf{T}^0 } \\
      %& F_{ \mathbf{Z} }
      \\};
  \path[-stealth]
  % the - argument removes the arrowhead
    (m-1-1) edge[] node [below] {(A3)} (m-1-2)

@@

    %(m-1-2) edge[dotted] node [right] {(L2)} (m-2-2)
            ;
\end{tikzpicture} % pic 1
\qquad
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     F_{ \widehat{\theta}^{(j)} } & F_{ \widehat{\theta}^0 }  \\
      \widehat{F}_{ \widehat{\theta}^{(j)} } & \\};
  \path[-stealth]
  % the - argument removes the arrowhead
    (m-1-1) edge[] node [below] {(L1)} (m-1-2)

    % diagonal line
	(m-2-1) edge[dashed] node [left] {(R2)} (m-1-1)

    (m-2-1) edge [dotted] node [below] {(T1)} (m-1-2)
            ;
\end{tikzpicture}
\end{center}
\end{figure}

<!-------------- Definition 1 --------------->
<!-------------- \setcounter{assump}{2} --------------->
\bigskip \begin{assump}[Resampling under the strong null] 
\label{cbt_def}
The resampling algorithm used to generate $\left( Z_{n1}^{(j)}, \dotsb, Z_{nK}^{(j)} \right)$ must generate identically and independently distributed (i.i.d.) observations, and it must ensure that $\mathbf{T}^{(j)} \xrightarrow[B \to \infty]{D} \mathbf{T}^0$, i.e.:
$$\lim_{B \to \infty} F_{\mathbf{T}^{(j)}} = F_{\mathbf{T}^0}$$
\end{assump}

This requirement has several critical implications. First, the resampled data must preserve the correlation structure of all variables in the dataset, except where the strong null dictates otherwise. Otherwise, the distribution of the test statistics will typically not be preserved. Second, just as the original data are assumed to respect the parametric assumptions of all $W$ hypothesis tests, the resampled data must be generated in a manner that also respects this parametric structure. Otherwise, hypothesis tests conducted on the resampled data may not preserve their nominal $\alpha$-levels, which again affects the distribution of the test statistics.

<!-------------- Example 1 ------------->
\bigskip
\begin{example}[A valid resampling algorithm for multiple linear regression] 
\label{ex:ols}
\normalfont
Suppose we conduct $W=2$ hypothesis tests using ordinary least squares (OLS) regressions of the first and second variables on the third variable, adjusting for the fourth:
\begin{align*}
Z_{n1} &= \beta_0 + \beta_1 Z_{n3} + \beta_2 Z_{n4} + \epsilon_{n1}\\
Z_{n2} &= \alpha_0 + \alpha_1 Z_{n3} + \alpha_2 Z_{n4} + \epsilon_{n2}
\end{align*}
with null hypotheses $H_{01}: \beta_1 = 0$ and $H_{02}: \alpha_1 = 0$, and assuming $\epsilon_{nw} \sim N(0, \sigma^2_w)$ for $w \in \{1,2\}$. A resampling algorithm \hl{[@westfalltext]} satisifying Assumption \ref{cbt_def} could proceed by first fixing the covariates $Z_{n3}$ and $Z_{n4}$ for all observations while setting the "outcomes" equal to a vector of residuals resampled with replacement. That is, letting $n'$ denote an observation sampled with replacement and letting hats denote the usual OLS estimates obtained from the original dataset, the resampled variables for observation $n$ are: 
\begin{align*}
Z_{n1}^{(j)} &:= \left( \widehat{Z}_{n'1} - Z_{n'1} \right)\\
Z_{n2}^{(j)} &:= \left( \widehat{Z}_{n'2} - Z_{n'2} \right)\\
Z_{n3}^{(j)} &:= Z_{n3}\\
Z_{n4}^{(j)} &:= Z_{n4}
\end{align*}
This resampling algorithm fulfills Assumption \ref{cbt_def} (\hl{proof in progress}). Note that even if the original data were not generated under the strong null, this resampling algorithm guarantees that $E \big[ Z_{nw}^{(j)} \; \vert \; Z_{n3} \big] = E \big[ Z_{nw}^{(j)} \big]$ for $w \in \{1,2\}$, implying the strong null. This algorithm also retains the distributional assumption on $\epsilon_{n1}$ and $\epsilon_{n2}$.
\end{example}

<!-------------- Example 2  ------------->
\bigskip
\begin{example}[An invalid resampling approach for multiple linear regression]
\normalfont
We now return to the setting of Example \ref{ex:ols}. An alternative resampling approach that is intuitive, but in fact violates Assumption \ref{cbt_def}, is to again fix $Z_{n3}$ and $Z_{n4}$ but to resample with replacement the outcome vectors $\left( Z_{n'1}, Z_{n'2} \right)$ rather than the residuals:
\begin{align*}
Z_{n1}^{(j)} &:= {Z}_{n'1}\\
Z_{n2}^{(j)} &:= {Z}_{n'2}\\
Z_{n3}^{(j)} &:= Z_{n3}\\
Z_{n4}^{(j)} &:= Z_{n4}
\end{align*}
Although this approach indeed enforces the strong null and preserves the correlation between the outcomes, it fails to preserve the correlation between the outcomes and the adjusted covariate, $Z_{n4}$, and thus does not recover the distribution of $\left( \widehat{\beta}_1^0, \widehat{\alpha}_1^0 \right)$.
\end{example}

<!-------------- Example 2 ------------->
\bigskip
\begin{example}[Another invalid resampling algorithm for multiple linear regression] 
\normalfont
Another incorrect alternative would be to bootstrap parametrically while constraining $\beta_1 = \alpha_1 = 0$ to enforce the strong null:
\begin{align*}
Z_{n1}^{(j)} &:= \widehat{\beta}_0 + \widehat{\beta}_2 Z_{n4} + \epsilon_{n1}^{(j)}\\
Z_{n2}^{(j)} &:= \widehat{\alpha}_0 + \widehat{\alpha}_2 Z_{n4} + \epsilon_{n2}^{(j)}\\
Z_{n3}^{(j)} &:= Z_{n3}\\
Z_{n4}^{(j)} &:= Z_{n4}
\end{align*}
where $\epsilon_{nw}^{(j)} \sim_{i.i.d.} N(0, \widehat{\sigma}^2_{\epsilon_{nw}})$ for $w \in \{ 1,2\}$. However, this sequential algorithm fails to preserve the correlation between $Z_{n1}$ and $Z_{n2}$, in turn failing to recover the distribution of $\left( \widehat{\beta}_1^0, \widehat{\alpha}_1^0 \right)$.
\end{example}

<!-------------- Remark 1 --------------->
\bigskip
\begin{remark}
\label{CMT_results}
\normalfont
For Assumption \ref{cbt_def} to hold, it is sufficient for $\mathbf{T}$ to be a continuous function of $\mathbf{Z}$ and for $\mathbf{Z}^{(j)} \xrightarrow[B \to \infty]{D} \mathbf{Z}^0$, i.e., $\lim_{B \to \infty} F_{\mathbf{Z}^{(j)}} = F_{\mathbf{Z}^0}$. Note that this condition is \emph{not} necessary for Assumption \ref{cbt_def} to hold; for example, under the residual resampling scheme of Example \ref{ex:ols}, we have $E \big[ Z_{n1}^{(j)} \big] = E \big[Z_{n2}^{(j)} \big] = 0$ regardless of $E \big[ Z_{n1} \big]$ and $E \big[Z_{n2}\big]$.
\end{remark}

<!-------------- Remark 2 --------------->
\bigskip \begin{remark}
\label{glivenko}
\normalfont
By the i.i.d. construction of the resampled data (Assumption \ref{cbt_def}) and the Glivenko-Cantelli theorem, the empirical distribution of the number of rejections in the resamples converges almost surely in $B$ to its true distribution:
$$\widehat{F}_{\widehat{\theta}^{(j)}} \xrightarrow[B \to \infty]{A.S.} F_{\widehat{\theta}^{(j)}} $$
\end{remark}

@@

<!-------------- Lemma 1 --------------->
\bigskip \begin{lemma}
\label{lemma3}
The number of rejections in the resamples converges in distribution in $N$ to the number of rejections in samples from the original population under the strong null:
$$\lim_{B \to \infty} F_{{ \widehat{\theta} }^{(j)}} = F_{{ \widehat{\theta}^0 }}$$

@@

\bigskip Now consider the distribution of $\widehat{\theta}^{(j)}$:
\begin{align*}
\lim_{B \to \infty} P \left( \widehat{\theta}^{(j)} = r \right) &= \lim_{B \to \infty} P \left( \sum_{w=1}^W 1 \Big\{ T_w^{(j)} > c_{w,\alpha} \Big\} = r \right) \\
&= \lim_{B \to \infty} \sum_{ \left( A_1, \dotsb, A_W \right) \in \mathcal{A} } P \left( T_1^{(j)} \in A_1, \dotsb, T_W^{(j)} \in A_W \right) \\
& \sum_{ \left( A_1, \dotsb, A_W \right) \in \mathcal{A} } P \left( T^0_1 \in A_1, \dotsb, T^0_W \in A_W \right) \tag{\text{from Assumption} \ref{cbt_def}}\\
&= P \left( \widehat{\theta}^0 = r \right)
\end{align*}
\end{proof}
\end{lemma}

<!-------------- Theorem 1 --------------->
\bigskip \begin{theorem} 
\label{theorem1}
The empirical distribution of the number of rejections in the resamples is consistent in $N$ and $B$ for the true distribution of the number of rejections under the strong null:
$$\widehat{F}_{\widehat{\theta}^{(j)}} \xrightarrow[B, N \to \infty]{P} F_{\widehat{\theta}^0} $$
\begin{proof}
Fix an arbitrarily small $\epsilon > 0$ and $\epsilon' > 0$. Remark \ref{glivenko} implies convergence in probability, so there exists a $B^{*}$ such that, for all $B > B^{*}$:
\begin{align*}
P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon / 2 \right) &< \epsilon'
\end{align*}
Similarly, from Lemma \ref{lemma3}, there exists an $N^{*}$ such that, for all $N > N^{*}$:
\begin{align*}
\left\vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \right\vert &< \epsilon / 2
\end{align*}
Thus, for all $B$ and $N$ such that $B > B^{*}$ and $N > N^{*}$:
\begin{align*}
P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right) &= P \left( \vert  \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } + F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right) \\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert + \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon \right)  \tag{triangle inequality}\\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon/2 \; \text{ or } \; \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon/2 \right) \\
&\le P \left( \vert \widehat{F}_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^{(j)} } \vert > \epsilon/2 \right) + P \left( \vert F_{ \widehat{\theta}^{(j)} } - F_{ \widehat{\theta}^0 } \vert > \epsilon/2 \right) \\
&< \epsilon' + 0
\end{align*}
\end{proof}
\end{theorem}

<!-------------------------- --------------------------------->
<!-------------- SECTION: GIBBS --------------->
<!-------------------------- --------------------------------->

\section{A general Gibbs resampling algorithm}
